Misc Code

### 2019-03-15 Misc Code.Rmd
Adding cross validation to miscelaneaous file

>>>>

###Cross Validation

```{r}
#
##crossv_sets
crossv_sets <- function(dtm){
  #Setup
  n_documents <- nrow(dtm)
  folding <- sample(rep(1:10, ceiling(n_documents))[seq_len(n_documents)]) #not very elegant

  #functions
  create_trainset <- function(Fold){
    train_set = dtm[folding != Fold,]
  }

  create_testset <- function(Fold){
    test_set  = dtm[folding == Fold,]
  }

  #create folds
  folds <-  data.frame(Fold = 1:10) %>%
    mutate(train_set = map(Fold, .f = create_trainset),
           test_set  = map(Fold, .f = create_testset))
  #
  ##Output
  return(folds)
}

#
##Testing Application:
a_test <- d_cast$overview[1:10,]

a <- crossv_sets(a_test)

b <- a %>%

  mutate(n_topic = 2) %>%

  mutate(model = list(n_topic, train_set) %>% pmap(my_LDA, control = my_control_fast))

```
